---
title: "Moorea Bleaching - May 2016 - Nutrients"
author: "Tom Adam, Deron Burkepile, Mary Donovan, et al"
date: "4/27/2018"
output: 
  rmarkdown::html_document:
    theme: sandstone
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
---

Write something introducing the project...  

## Initialization
```{r initialization, echo=TRUE, warning=FALSE}
rm(list=ls())
home <- getwd()

library(tidyverse)
library(mgcv)
library(MuMIn)
```
  
## Data import and setup
```{r data import and setup}
data <- read.csv(file.path(home,'data','Poc_Acrop_bleaching_all_data_wTemp.csv'))
source('myplotcorr.R')

data <- rename(data, dist_crest=Distsance.to.crest)
data <- rename(data, dist_shore=Distance_to_shore)
data <- rename(data, dist_pass=Distance_to_pass)
data <- rename(data, dist_deep=Distance_to_deep_lagoon_water)
data <- rename(data, dist_pop=Distance_to_population_center)
data <- rename(data, tot_N=Total..N)
data <- rename(data, d15N=d15NNorm..)

# levels incorrect for bleaching column
data$Bleached[data$Bleached==''] <- NA
data$Bleached <- as.character(data$Bleached); data$Bleached <- as.factor(data$Bleached)
levels(data$Bleached)
data$bleach.z <- 0
data$bleach.z[data$Bleached=='Y'] <- 1
data$bleach.z[data$Bleached=='N'] <- 0

## points 20 and 85 are missing nutrient data - Tom to check
```


## Correlations among variables
```{r correlations}
# set up color ramp
colsc=c(rgb(241, 54, 23, maxColorValue=255), 'white', rgb(0, 61, 104, maxColorValue=255))
colramp = colorRampPalette(colsc, space='Lab')
colorrs = colramp(100)
# save correlations
mycorgo <- cor(data[c('Depth_m',"dist_crest","dist_shore","dist_pass","dist_deep","dist_pop","Mean_wave_power","SD_wave_power","tot_N" ,"d15N","cumstress")],use='pairwise.complete.obs')
#plot
my.plotcorr(mycorgo, col=colorrs[((mycorgo + 1)/2) * 100], diag='ellipse', main='', upper.panel="number", mar=c(0,0,0,0),cex=0.5)

```
  
Distance to crest and distance to shore are correlated (rho=`r round(cor(data[c('dist_crest','dist_shore')])[2],2)`), so we are going to use distance to crest only. Distance to pass and distance to deep lagoon water are also correlated (rho=`r round(cor(data[c('dist_pass','dist_deep')])[2],2)`), so we are going to use distance to pass in the model.

## Center continuous explanatory data
```{r}
c.vars <- data[c('Depth_m',"dist_crest","dist_shore","dist_pass","dist_deep","dist_pop","Mean_wave_power","SD_wave_power","tot_N" ,"d15N","cumstress")]
c.vars.s <- c.vars
for(i in 1:length(c.vars)) c.vars.s[i] <- scale(c.vars[i][,1])
colnames(c.vars.s) <- paste(colnames(c.vars),'.s',sep='')
data <- cbind(data, c.vars.s)
```

## Construct full GAMM model
```{r}
dat <- data[data$Taxa=='Pocillopora',]
dat <- dat[!is.na(dat$bleach.z),]
dat <- dat[!is.na(dat$tot_N),]
dat <- dat[!is.na(dat$Depth_m),]
gam.poc <- gamm(bleach.z ~ s(Depth_m.s,k=4) + s(dist_crest.s,k=4) + s(dist_pass.s,k=4) + s(dist_pop.s,k=4) + Mean_wave_power.s + SD_wave_power.s + s(cumstress.s,k=4) + s(tot_N.s,k=4) + s(d15N.s, k=4),random=list(Habitat=~1), family='binomial', data=data[data$Taxa=='Pocillopora',], niterPQL=100)

gam.poc <- bam(bleach.z ~ s(Depth_m.s,k=4) + s(dist_crest.s,k=4) + s(dist_pass.s,k=4) + s(dist_pop.s,k=4) + Mean_wave_power.s + SD_wave_power.s + s(cumstress.s,k=4) + s(tot_N.s,k=4) + s(d15N.s, k=4) + s(Habitat,by=Island_shore,bs='re') + s(Point,bs='re'), family='binomial', data=dat, na.action='na.fail')
summary(gam.poc)
```

Model improvements to do:  
- add spatial autocorrelation --- AND/OR deal with the hierarchical aspects???
- include colony size

## Model selection
```{r}
gam.poc.dredge <- dredge(gam.poc)
```

